---
title: "PREDICTION FOR NEW FUTURE HOME"
output: html_notebook
---
WE ALL HAVE AN HOPE TO BUILD OR TO BUY A PROPERTY OF OUR OWN. 
THIS IS JUST AN PUBLICATION OF FUTURE PREDICTION OF OUR PROPERTY.

This is published by C.AKKIL ANAND.

THANKS TO MR. THULSIDASS.

THANKS TO KAAGLE.COM (FOR REFERENCE DATA).




REFERENCE DATA:
  
   This is the data which is refered to our prediction 
```{r}
View(House_Price)
```

SUMMARY OF THE DATA:
   
   This sample data consists of bedrooms, bathrooms,
   livivg area, floors, overall area, and price.
   
   These are some eesential data to predict our future value of the property.

```{r}
summary(House_Price)
```
 STRUCTURE OF OUR DATA:

  These are some statistically used format.
  
  just for the refernce for reserch purpose


```{r}
str(House_Price)
```


 GRAPHICAL REPRESENTATION OF SAMPLE DATA:

  1.BARPLOT OF SAMPLE DATA:


```{r}
table(House_Price$bedrooms)
barplot(table(House_Price$bedrooms),xlab = 'no.of bedroooms', ylab = 'frequency',main ='MOST PREFERED NO.OF.BEDROOM',col=c('blue','green','red','orange','yellow'))
```
this barpolt reveals that "MOST PREFERED NO.OF BEDROOMS are "3" and "4".  
                     
```{r}
table(House_Price$sqft_living)
plot(table(House_Price$sqft_living),xlab='living area',ylab = 'FREQUENCY',main = 'MOST PREFERED LIVING AREA',col=c('light green'))
```
This barplot results that the "MOST PREFERED LIVING AREA" is between : 1000 TO 2500 sq.ft
          
          
          
          
          
          
 CORRELATION OF THE SAMPLE DATA:

 This the states that variable which have strong relationship between the price.
 
 IS USED IN THE PROCESS OF PREDICTION WHICH MAY BE HELPFUL. 
```{r}
cor(House_Price)
```


CORRELATION GRAPH FOR THE RELATED VALUES:

```{r}
par(mfrow=c(1,2))
library(corrplot)
al=cor(House_Price)
corrplot(al)
scatter.smooth(House_Price$sqft_living,House_Price$price,main="PRICE AND SQ.FT LIVING",col=c("purple"))
```
 as we state that "PRICE" is our main part prediction we take best correlation of it, that "correlation between SQ.FT OF LIVING AND PRICE"
 
 
 Other correlation are between bathroon and sq.ft of living.


REGRESSION FOR THE SAMPLE DATA:

```{r}
myre=lm(House_Price$price~House_Price$bedrooms+House_Price$bathrooms+House_Price$sqft_living+House_Price$sqft_lot+House_Price$floors)
summary(myre)
```

CALCULATING THE COEFFIENTS RELATED FOR THE MANNUAL CALCULATION

```{r}
cor(House_Price$sqft_living,House_Price$price)
```

```{r}
par(mfrow=c(2,2))
plot(myre,col="light blue")
abline(myre)
```


```{r}
myre$fitted.values
```


 
```{r}
plot(House_Price$price,myre$fitted.values,col="yellow")
abline(House_Price$price,myre$fitted.values)
```


COEFFIENTS:
 
```{r}
coef(myre)
coef(myre)
```
from these coeffients we calculate future value by substuting in linear regression equation
 
 
 
 
 
 
 
 
 

 

































